Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalnew\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-06-22 ms.tex
fp table edits

\subsection{Stellar Models}
\label{sec:stellarparams}
To convert the observed photometric data into physical properties for each
star, we used the new publicly available \texttt{isochrones} Python module\footnote{
\url{http://github.com/timothydmorton/isochrones}}, a general-purpose
interpolation tool for the fitting of stellar models to photometric or spectroscopic
parameters.
This software does trilinear interpolation in mass--age--\feh\ space for any
given set of model grids, thus being able to predict the value for any
physical or photometric property provided by the models at any values of
mass, age, and \feh\ within the boundaries of the grid.

>>>>

\subsection{Stellar Models}
\label{sec:stellarparams}
To convert the observed photometric data into physical properties for each
star, we used the new publicly available \texttt{isochrones} Python module\footnote{
\url{http://github.com/timothydmorton/isochrones}}, a general-purpose
interpolation tool for the fitting of stellar models to photometric or spectroscopic
parameters \citep{isochrones}.
This software does trilinear interpolation in mass--age--\feh\ space for any
given set of model grids, thus being able to predict the value for any
physical or photometric property provided by the models at any values of
mass, age, and \feh\ within the boundaries of the grid.

### 2015-06-22 table_fpp.tex
edited fpp table
fpp table note edits
fp table edits

@@

@@

identified in the literature are marked as planets even if FPP is not 
below 1\% threshold.}

>>>>

 \color{red} 201555883.01  & \color{red}  $0.94$  & \color{red}   -  & \color{red}   --  & \color{red}   --  & \color{red}   --  & \color{red}   --  & \color{red}  --  & \color{red}  FP\tablenotemark{b} \\

@@

 \color{red} 201929294.01  & \color{red}  $3.12$  & \color{red}   -  & \color{red}   --  & \color{red}   --  & \color{red}   --  & \color{red}   --  & \color{red}  --  & \color{red}  FP\tablenotemark{b}  

@@

identified in the literature are marked.}
